\documentclass[letterpaper,11pt]{article}

\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[russian,english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------
\begin{center}
  \textbf{\Huge \scshape Igor Polyakov} \\ \vspace{3pt}
    \small
    \faAt \hspace{.5pt} \href{mailto:igorpolyakov@protonmail.com}{igorpolyakov@protonmail.com}
    $|$
    \faTelegram \hspace{.5pt} \href{https://t.me/hotorcelexo}{@hotorcelexo}
    $|$
    \faLinkedinIn \hspace{.5pt} \href{https://www.linkedin.com/in/polyakov-igor-b63497133/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/IgorPolyakov}{GitHub}
    $|$
    \faMapPin \hspace{.5pt} Saint Petersburg, Russia
\end{center}

%----------- WORK EXPERIENCE -----------
\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kupibilet}{Saint Petersburg, Russia}
      {Backend Engineer}{Nov 2018 \textbf{--} Jul 2023}
        \resumeItemListStart
          \resumeItem{Worked on account service improvements, personal data and card data storage and processing. Stack: Go / MySQL / Iris / GORM.}
          \resumeItem{Improved the messaging service. Stack: Go / RabbitMQ / Iris. Implemented i18n for messages using Gobuffalo Plush.}
          \resumeItem{Developed from scratch an information system for the "seat selection" service. Stack: Go / Gin / OpenAPI.}
          \resumeItem{Supported and developed a service for working with bank cards, necessary to comply with PCI DSS norms. Stack: Go / Mux / Redis / AES}
          \resumeItem{Participated in PCI DSS audit, implemented security tools like Nancy for safe user data handling.}
          \resumeItem{Developed and improved the existing API for booking and selling air tickets. Stack: Ruby 2 / MongoDB 3.}
          \resumeItem{Implemented and supported integrations with payment systems (Tinkoff, Checkout.com, YooKassa, Pay2Me). Stack: Ruby / Dry-* / PSQL / Roda / ROM.}
          \resumeItem{Connected and operated online cash registers, generating fiscal documents. Stack: Orange Data / Ruby.}
          \resumeItem{Added monitoring and visualization of application and infrastructure performance, including graphs, alerts, and custom metrics. Stack: Prometheus / Grafana / Elasticsearch / Logstash / Kibana / Sentry.}
          \resumeItem{Implemented tools and approaches for internationalization of the main API. Stack: Rails-i18n / Lokalise.com / Weblate.org / I18n-tasks.}
          \resumeItem{Solved tasks related to the introduction of continuous integration and continuous delivery (CI/CD), writing scenarios for static analysis, testing, and deploying code to test servers. Stack: Self-hosted GitLab / Traefik / Docker / Docker-compose / HAProxy.}
          \resumeItem{Supported the API for generating landing pages (SEO). Stack: Ruby 2 / Rails 5 / MongoDB 3 / Bootstrap.}
          \resumeItem{Supported and developed parsers needed for business, such as price parsers, IATA objects, etc. Stack: Ruby / Selenium / Curl.}
          \resumeItem{Supported and developed the search suggestions service (suggest). Stack: Elixir / Cowboy.}
          \resumeItem{Supported internal tools that facilitate developers' lives. Stack: Crystal / JIRA-API / GitLab-API / Slack-API.}
        \resumeItemListEnd
    \resumeSubheading
      {Elecard}{Tomsk, Russia}
      {Software Engineer}{Aug 2017 \textbf{--} Nov 2018}
        \resumeItemListStart
          \resumeItem{Improvements to the existing project Boro Elecard. Stack: Rails 4 / jQuery.}
          \resumeItem{Development of an internal service for generating and managing digital certificates (X.509). Stack: Rails 4 / OpenSSL.}
          \resumeItem{Development and support of JRPC server. Stack: Plain Ruby.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
%----------- EDUCATION -----------
\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tomsk State University of Control Systems and Radioelectronics}{Tomsk, Russia}
      {Engineer in Automation and Production (Computer Vision);   \textbf{Computer Systems}}{Sep 2010 \textbf{--} Jan 2015}
    \resumeSubheading
      {Institute of Strength Physics and Materials Science SB RAS}{Tomsk, Russia}
      {Postgraduate in Computer Science and Engineering;   \textbf{Computer Science and Engineering}}{Sep 2015 \textbf{--} Jan 2017}
  \resumeSubHeadingListEnd
%----------- SKILLS -----------
\section{Skills}
\vspace{2pt}
\resumeSubHeadingListStart
\small{\item{
\textbf{Programming Languages:} Go, Ruby, Elixir, SQL \vspace{3pt}
\textbf{Technologies:} Linux, Git, Docker, PostgreSQL, MongoDB, CI/CD \vspace{3pt}
\textbf{Languages:} Russian (Native), English (Elementary)
}}
\resumeSubHeadingListEnd

%----------- EDUCATION (Update)-----------
\section{Certificates}
\vspace{2pt}
\resumeSubHeadingListStart
\resumeSubItem{Asynchronous Architecture Course, School of Strong Programmers, 2022}
\resumeSubHeadingListEnd
\end{document}
